Conjure: Summoning Proxies from Unused Address Space

### 2019-09-26 paper/paper.tex
more minor edits

\paragraph{\texttt{obfs4}}
Unlike previous versions of obfsproxy, the \texttt{obfs4} protocol is designed to
be resistant to active probing
attacks, requiring the client prove knowledge of a secret before the server will
respond. We verified that naive active probing attacks (where we attempt to
connect to an \texttt{obfs4} server without knowledge of the secret and see if
it provides proxy access) do not work
against \texttt{obfs4}. In addition, although China is effective at blocking
\texttt{obfs3}, the more recent probe-resistant \texttt{obfs4} remains a viable
proxy in the country

@@

One obvious future direction is to study new options for registration and proxy transport. For instance, while 
\scheme currently uses a refraction networking covert channel for registration, we could potentially 
cut down on the overhead of one-time registration by using port-knocking or using a 
Telex-style~\cite{telex11} tag (in the Client Hello rather than Application Data).

>>>>

\paragraph{\texttt{obfs4}}
Unlike previous versions of obfsproxy, the \texttt{obfs4} protocol is designed to
be resistant to active probing
attacks, requiring the client prove knowledge of a secret before the server will
respond. We verified that naive active probing attacks (where we attempt to
connect to an \texttt{obfs4} server without knowledge of the secret and see if
it provides proxy access) do not work
against \texttt{obfs4}. In addition, although China is effective at blocking
\texttt{obfs3}, the more recent probe-resistant \texttt{obfs4} remains a viable
proxy in the country.\footnote{E.g., \url{https://metrics.torproject.org/userstats-bridge-combined.html?start=2019-06-27&end=2019-09-25&country=cn} shows \texttt{obfs4} clients from China successfully using Tor.}

@@

One obvious future direction is to study new options for registration and proxy transport. For instance, while 
\scheme currently uses a TapDance- style covert channel for registration, we could potentially 
cut down on the overhead of one-time registration by using port-knocking or using a 
Telex-style~\cite{telex11} tag (in the ClientHello rather than Application Data).
